Evaluation of performances

### 2020-05-29 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

```{r aggr-perf}
# Aggregate performances and add standard error column.
df_perf %<>%
  group_by(task.id, learner.id, filter) %>%
  mutate(rmse_aggr = round(mean(rmse), 3)) %>%
  mutate(se = round(sd(rmse), 3)) %>%
  select(-rmse, iter) %>%
  ungroup()
```

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGB Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for selected learner-filter settings across folds for task HR-NRI-VI, sorted ascending by RMSE",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )

>>>>

```{r aggr-perf}
# Aggregate performances and add standard error column.
df_perf %<>%
  dplyr::group_by(task.id, learner.id, filter) %>%
  dplyr::mutate(rmse_aggr = round(mean(rmse), 3)) %>%
  dplyr::mutate(se = round(sd(rmse), 3)) %>%
  dplyr::select(-rmse, iter) %>%
  dplyr::ungroup()
```

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate("\\#" = case_when(
    Plot == "Laukiz1" ~ ceiling(`Features (\\%)` * 559),
    Plot == "Laukiz2" ~ ceiling(`Features (\\%)` * 451),
    Plot == "Luiando" ~ ceiling(`Features (\\%)` * 301),
    Plot == "Oiartzun" ~ ceiling(`Features (\\%)` * 497),
  )) %>% 
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", "\\#", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\specialcell{", df_tbl[[1]][first], "}}")
# remove redundant midrule from first entry
df_tbl[[1]][first][1] = gsub("\\\\midrule", "", df_tbl[[1]][first][1])

table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for selected learner-filter settings across folds for task HR-NRI-VI, sorted ascending by RMSE",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 0, 2)
  )
